---
title: "Griffiths et al experiment analysis"
author: "Mary OConnor"
date: '2019-09-13'
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(reshape2)
library(plyr)
library(stringr)
#library(nlme)
library(MuMIn)
library(knitr)
library(captioner)
knitr::opts_chunk$set(echo = FALSE)
```

```{r load data, echo=FALSE}
smith.bio <- read.csv("../data/Smith.csv") # from experiment
compare <- read.csv("../data/choked_seagrass_smithora.csv")
sites <- read.csv("../data/choked_sites.csv")
smith.expt <- read.csv("../data/Transplant_raw_smithora_wt.csv")
grazertraits <- read.csv("../data/grazertraitsmaster.csv")
#grazers <- read.csv("./data/Grazers_EdgeVSInterior_V1_Aug09_2017.csv")
# in sept 2019 i dug through emails. i think we should use this grazer file: 
grazers <- read.csv("../data/Grazers_EdgeVSInterior_2017.csv")
grazer_eelgrass <- read.csv("../data/Grazers_Eelgrass_Data_EdgeVSInterior_2017.csv")
grazer_taxa <- read.csv("../data/invert.taxa.csv")
```

```{r compare edge data not in use}
### compare
## looks like there are zostera and smithora data that match the grazer samples. So let's use that and not this file, which appears to be only the July eelgrass samples.
## from meadow surveys, identify edge and inner samples
edge <- filter(compare, site == "choked_edge_wolf")
inner <- filter(compare, site == "choked_inner_wolf")
compare_edge <- bind_rows(inner,edge)

###Making data nicer for plotting
#head(compare)
#View(compare)
compare_edge2 <- compare_edge
compare_edge2$site <- as.character(compare_edge2$site)
compare_edge2$site[compare_edge$site == "choked_edge_wolf"] <- "Edge"
compare_edge2$site <- as.character(compare_edge2$site)
compare_edge2$site[compare_edge$site == "choked_inner_wolf"] <- "Interior"
```

```{r survey data}
survey2_eg <- grazer_eelgrass %>%
  select(-quadrat.location)%>%
  select(-date)

survey2_eg$Sample_time <- as.character(survey2_eg$Sample_time)
survey2_eg$Sample_time[survey2_eg$Sample_time == "July"] <- "2"
survey2_eg$Sample_time <- as.character(survey2_eg$Sample_time)
survey2_eg$Sample_time[survey2_eg$Sample_time == "June"] <- "1"
survey2_eg$Sample_time <- as.numeric(survey2_eg$Sample_time)

survey2_eg$Sample_mo <- survey2_eg$Sample_time
survey2_eg$Sample_mo[(survey2_eg$Sample_mo)=="1"] <- "June"
survey2_eg$Sample_mo[(survey2_eg$Sample_mo)=="2"] <- "July"

survey2_eg <- survey2_eg %>% 
  mutate(ratio = as.numeric(smithora.dry.weight.grams)/zostra.final.dry.macro.weight.grams)
```

```{r mean mid sd max function}
## function to estimate sds for boxplots
min.mean.sd.max <- function(x) {
  r <- c(min(x), mean(x) - sd(x), mean(x), mean(x) + sd(x), max(x))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}
```

## survey results for Z density
A) Shoot density (moved to supplementary material)
```{r survey shoot density models}
hist(survey2_eg$number.shoots.quadrat)
moda <- lm(number.shoots.quadrat ~ 1, data = survey2_eg)
modb <- lm(number.shoots.quadrat ~ 1 + Zone, data = survey2_eg)
modc <- lm(number.shoots.quadrat ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(number.shoots.quadrat ~ 1 + Zone*Sample_time, data = survey2_eg)
model.sel(moda, modb, modc, modd)
mavg <- model.avg(modd, modb, moda)

summary(modd)

Z.june.edge <- coef(mavg)[1]*16
Z.jul.edge <- coef(mavg)[1]*16 + coef(mavg)[3]*16
Z.jul.int <- coef(mavg)[1]*16 + coef(mavg)[4]*16


```

FIGURE 2: ZOSTERA, SMITHORA and GRAZER ABUNDANCE at transplant sites before experiment

```{r shoot density plot}
shoot.density <- ggplot(survey2_eg, aes(x = Zone, y = number.shoots.quadrat*16)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  geom_boxplot(size = 1, fill = "transparent") + 
  scale_y_continuous(name = "Zostera Shoots (N/ m^2)") +
  theme_bw() + 
  theme(panel.grid = element_blank()) + 
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("Zone")) + 
  #geom_text(label = "A", x = 2.4, y = 15) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

shoot.density

ggsave("shoot.density.jpg", plot = shoot.density, width = 6, height = 3)
```

## survey results for invertebrate density
```{r}

```

## B) Zostera shoot dry weight
```{r Zostera dry weight figure}
shoot.dwt <- ggplot(survey2_eg, aes(x = Zone, y = zostra.final.dry.macro.weight.grams*16)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Zostera shoot dry weight (g/m^2)") +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  theme_bw() + 
  theme(panel.grid = element_blank()) + 
  xlab(expression("Zone")) + 
  #geom_text(label = "A", x = 2.4, y = 30) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

shoot.dwt
ggsave("shoot.dwt.jpg", plot = shoot.dwt, width = 6, height = 3)
```

Zostera above ground dry weight
```{r Zostera dry weight models}
#hist(compare_edge2$total.dry.macro.weight)
hist(survey2_eg$zostra.final.dry.macro.weight.grams)
moda <- lm(zostra.final.dry.macro.weight.grams ~ 1, data = survey2_eg)
modb <- lm(zostra.final.dry.macro.weight.grams ~ 1 + Zone, data = survey2_eg)
modc <- lm(zostra.final.dry.macro.weight.grams ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(zostra.final.dry.macro.weight.grams ~ 1 + Zone*Sample_time, data = survey2_eg)
model.sel(moda, modb, modc, modd)

summary(modc)
Zjune.edge <- (coef(modc)[1] + coef(modc)[3])*16
Zjul.edge <- (coef(modc)[1] + coef(modc)[3]*2)*16
Zjune.int <- (coef(modc)[1] + coef(modc)[3] + coef(modc)[2])*16
Zjul.int <- (coef(modc)[1] + coef(modc)[3]*2 + coef(modc)[2])*16
```

B) Smithora load (dry weight)
```{r Smithora load models}
#hist(compare_edge2$total.dry.macro.weight)
mod1 <- lm((smithora.dry.weight.grams/zostra.final.dry.macro.weight.grams) ~ site, data = survey2_eg)
anova(mod1)

hist(log(survey2_eg$ratio))

moda <- lm(ratio ~ 1, data = survey2_eg)
modb <- lm(ratio ~ 1 + Zone, data = survey2_eg)
modc <- lm(ratio ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(ratio ~ 1 + Zone*Sample_time, data = survey2_eg)
model.sel(moda, modb, modc, modd)

mavg <- model.avg(modd, modb, moda)

summary(modb)

Z.june.edge <- coef(mavg)[1]*16
Z.jul.edge <- coef(mavg)[1]*16 + coef(mavg)[3]*16
Z.jul.int <- coef(mavg)[1]*16 + coef(mavg)[4]*16
```

```{r Smithora load plot}
smithora <- ggplot(survey2_eg, aes(x = Zone, y = ratio)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = expression(paste(italic("Smithora"), " (g dry wt / g Zostera dry wt)")), limits = c(0, 0.5)) +
  theme_bw() + 
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  theme(panel.grid = element_blank()) + 
  xlab(expression("Zone")) + 
  #geom_text(label = "B", x = 2.4, y = 0.5) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

smithora

ggsave("smithora.jpg", plot = smithora, width = 6, height = 3)
```

D) GRAZER ABUNDANCE

```{r invertebrate data} 
#found i think the final grazer file in an email from coreen; using that here and cleaning it.
# I can match the grazer data with the eelgrass data from the same plots!
grazers[is.na(grazers)] <- 0
grazers1 <- grazers %>%
  filter(Seagrass.ASU != "ASU") %>%
  #select(-month_replicate_meadow.position) %>%
  select(-Seagrass.ASU) %>%
  select(-Distance.along.transect..m.)%>%
  select(-identifyer)%>%
  select(-Date.collected)%>%
  select(-size..mm.)
grazers1 <- melt(grazers1, id = c(1,2,3,4))
names(grazers1) <- c("Sample_ID","Sample_time", "Site", "Zone", "Species", "Abundance")
grazers3 <- ddply(grazers1, .(Sample_ID, Site, Zone, Sample_time, Species), summarise, sum(Abundance))
grazers3$N <- grazers3[,6]
inverts <- grazers3
inverts2 <- merge(inverts, grazer_taxa, by.x = "Species", by.y = "taxon.name")
inverts_table <- ddply(inverts, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(inverts_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","inverts_N")

grazers4 <- inverts2 %>%
  filter(grazer == "y")
grazers_table <- ddply(grazers4, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(grazers_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","grazers_N")

grazers_gastropod <- grazers4 %>%
  filter(phylum == "mollusca")
gastropod_table <- ddply(grazers_gastropod, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(gastropod_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","gastro_N")

grazers_crustacean <- grazers4 %>%
  filter(phylum == "arthropoda")
crustacean_table <- ddply(grazers_crustacean, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(crustacean_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","crust_N")

space_comp <- inverts2 %>%
  filter(Species == "mytilus", phylum == "bryozoa")

#names(grazers4) <- c("Sample_ID", "Site", "Zone", "Sample_time", "Species", "Abundance")

```

```{r combine invert data with shoot data}
# ok now merge grazer file with the eelgrass file
combined <- merge(survey2_eg, inverts_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", no.dups = TRUE)
combined2 <- merge(combined, grazers_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", no.dups = TRUE)
combined3 <- merge(combined2, gastropod_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", suffixes = c(".c", ".g"))
combined4 <- merge(combined3, crustacean_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", suffixes = c(".t", ".cr"))

combined <- combined4 %>% 
  mutate(gpgT = inverts_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgG = grazers_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgGa = gastro_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgC = crust_N/zostra.final.dry.macro.weight.grams)

```

```{r plots for combined factors}
plot(zostra.final.dry.macro.weight.grams ~ number.shoots.quadrat, data = combined)
```


```{r invert plots}
#hist(log(combined$Abundance))
grazerfigA <- ggplot(combined, aes(x = Zone.y, y = gpgT)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Invertebrates (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigA
ggsave("Inverts.jpg", plot = grazerfigA, width = 6, height = 2.5)

grazerfigB <- ggplot(combined, aes(x = Zone.y, y = gpgG)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Grazers (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigB
ggsave("Grazers.jpg", plot = grazerfigB, width = 6, height = 2.5)


grazerfigC <- ggplot(combined, aes(x = Zone.y, y = gpgGa)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Gastropod Grazers (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigC
ggsave("Gastropods.jpg", plot = grazerfigC, width = 6, height = 2.5)

grazerfigD <- ggplot(combined, aes(x = Zone.y, y = gpgC)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Crustaceans Grazers (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("Zone")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigD
ggsave("Crustaceans.jpg", plot = grazerfigD, width = 6, height = 2.5)
```

```{r invert models}
moda <- lm(gpgT ~ 1, data = combined)
modb <- lm(gpgT ~ 1 + Zone.y, data = combined)
modc <- lm(gpgT ~ 1 + Zone.y + Sample_time.x, data = combined)
modd <- lm(gpgT ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(moda, modb, modc, modd)
mavg <- model.avg(modd, moda)
summary(mavg)
summary(modd)

modGa <- lm(gpgG ~ 1, data = combined)
modGb <- lm(gpgG ~ 1 + Zone.y, data = combined)
modGc <- lm(gpgG ~ 1 + Zone.y + Sample_time.x, data = combined)
modGd <- lm(gpgG ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(modGa, modGb, modGc, modGd)
mavGg <- model.avg(modGd, modGa)
summary(mavGg)
summary(modGd)

modCa <- lm(gpgC ~ 1, data = combined)
modCb <- lm(gpgC ~ 1 + Zone.y, data = combined)
modCc <- lm(gpgC ~ 1 + Zone.y + Sample_time.x, data = combined)
modCd <- lm(gpgC ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(modCa, modCb, modCc, modCd)
mavCg <- model.avg(modCd, modCa)
summary(mavCg)
summary(modCd)

modGaa <- lm(gpgGa ~ 1, data = combined)
modGab <- lm(gpgGa ~ 1 + Zone.y, data = combined)
modGac <- lm(gpgGa ~ 1 + Zone.y + Sample_time.x, data = combined)
modGad <- lm(gpgGa ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(modGaa, modGab, modGac, modGad)
mavGag <- model.avg(modGad, modGaa)
summary(mavCg)
summary(modGab)
```


```{r grazers and smithora plot}
grazersmith <- ggplot(combined, aes(x = gpg, y = ratio, color = Sample_mo)) + 
  geom_point(size=3) +
  #geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  #stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  #scale_y_continuous(name = "Epifaunal Grazer Density (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("grazers / g Zostera")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazersmith
```

```{r models for smithora load}
moda <- lm(ratio ~ 1, data = combined)
modb <- lm(ratio ~ 1 + Zone.y, data = combined)
modc <- lm(ratio ~ 1 + Zone.y + Sample_time.x, data = combined)
modd <- lm(ratio ~ 1 + Zone.y*Sample_time.x, data = combined)
mode <- lm(ratio ~ 1 + Zone.y*Sample_time.x + gpg, data = combined)
modf <- lm(ratio ~ 1 + Zone.y*Sample_time.x + gpg + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = combined)
modg <- lm(ratio ~ 1 + Zone.y + Sample_time.x + gpg + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = combined)
modh <- lm(ratio ~ 1 + Zone.y + Sample_time.x + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = combined)
modi <- lm(ratio ~ 1 + Zone.y + Sample_time.x + zostra.final.dry.macro.weight.grams, data = combined)
modj <- lm(ratio ~ 1 + Zone.y + Sample_time.x + number.shoots.quadrat, data = combined)
modk <- lm(ratio ~ 1 + Zone.y + Sample_time.x + gpg, data = combined)
modl <- lm(ratio ~ 1 + Zone.y + gpg, data = combined)
modm <- lm(ratio ~ 1 + gpg, data = combined)
modn <- lm(ratio ~ 1 + number.shoots.quadrat, data = combined)
modo <- lm(ratio ~ 1 + zostra.final.dry.macro.weight.grams, data = combined)
modp <- lm(ratio ~ 1 + gpg + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = combined)
model.sel(moda, modb, modc, modd, mode, modf, modg, modh, modi, modj, modk, modl, modm, modn, modo, modp)
```


## FIGURE 3: Smithora results post experiment - remake this figure. april 5th: i'm not sure if it still needs to be remade - i have to check this.
```{r experiment results}
smith.expt$Source <- revalue(smith.expt$Source, c("Edge"="Edge (high Smithora)",  "Interior"="Interior (low Smithora)"))
smith.expt$Source <- as.factor(smith.expt$Source)
smith.expt$Type <- revalue(smith.expt$Category.in.transplant, c("Ambient"="Unmanip.", "Experiment"="Transplanted", "Control"="Control"))
smith.expt$Type <- as.factor(smith.expt$Type)
smith.expt$ratio <- smith.expt$Ratio.smithora.leaves
smith.expt$Final.Zone <- smith.expt$Final.Location

experiment <- ggplot(smith.expt[(smith.expt$Type != "Unmanip."),], aes(x = Type, y = ratio)) + 
geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
facet_wrap(~Source) + 
theme_bw() + 
theme(panel.grid = element_blank()) + 
theme(strip.background = element_rect(fill="white")) + 
scale_y_continuous(name = expression(paste(italic("Smithora"), " (g dry wt / g Zostera dry wt)")), limits = c(-0.1, 1), breaks = c(0, 0.5, 1), labels = c(0, 0.5, 1)) +
xlab("") +
labs(title = "Site of Experimental Planting") 

experiment
ggsave("experiment.jpg", plot = experiment, width = 6, height = 3)
```

##Experimental analysis: 

#first analyze control vs unmanipulated
```{r}
hist((smith.expt[(smith.expt$Type != "Transplanted"),]$ratio))
mod1 <- lm((smith.expt[(smith.expt$Type != "Transplanted"),]$ratio) ~ smith.expt[(smith.expt$Type != "Transplanted"),]$Type + smith.expt[(smith.expt$Type != "Transplanted"),]$Source)
anova(mod1)
```

```{r two way anova}
mod1 <- lm()
```

# then analyze control v transplanted
```{r}
hist(log(smith.expt[(smith.expt$Type != "Unmanip."),]$ratio + 1))
mod2 <- lm(log(ratio + 1) ~ Type*Source, data = smith.expt[(smith.expt$Type != "Unmanip."),])
summary(mod2)
```
