---
title: "Griffiths et al experiment analysis"
author: "Mary OConnor"
date: '2019-09-13'
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(reshape2)
library(plyr)
library(stringr)
#library(nlme)
library(MuMIn)
library(knitr)
library(captioner)
library(vegan)
library(viridis)
library(ggpubr) # multi-plot visualizations
knitr::opts_chunk$set(echo = FALSE)
```

```{r load data, echo=FALSE}
smith.bio <- read.csv("../data/Smith.csv") # from experiment
compare <- read.csv("../data/choked_seagrass_smithora.csv")
sites <- read.csv("../data/choked_sites.csv")
smith.expt <- read.csv("../data/Transplant_raw_smithora_wt.csv")
grazertraits <- read.csv("../data/grazertraitsmaster.csv")
#grazers <- read.csv("./data/Grazers_EdgeVSInterior_V1_Aug09_2017.csv")
# in sept 2019 i dug through emails. i think we should use this grazer file: 
grazers <- read.csv("../data/Grazers_EdgeVSInterior_2017.csv")
eelgrass_preexpt_survey <- read.csv("../data/Grazers_Eelgrass_Data_EdgeVSInterior_2017.csv")
grazers_coreen <- read.csv("../data/ASUdata.csv")
grazer_taxa <- read.csv("../data/invert.taxa.csv")
```

```{r compare edge data not in use}
### compare
## looks like there are zostera and smithora data that match the grazer samples. So let's use that and not this file, which appears to be only the July eelgrass samples.
## from meadow surveys, identify edge and inner samples
edge <- filter(compare, site == "choked_edge_wolf")
inner <- filter(compare, site == "choked_inner_wolf")
compare_edge <- bind_rows(inner,edge)

###Making data nicer for plotting
#head(compare)
#View(compare)
compare_edge2 <- compare_edge
compare_edge2$site <- as.character(compare_edge2$site)
compare_edge2$site[compare_edge$site == "choked_edge_wolf"] <- "Edge"
compare_edge2$site <- as.character(compare_edge2$site)
compare_edge2$site[compare_edge$site == "choked_inner_wolf"] <- "Interior"
```

```{r survey data}
survey2_eg <- eelgrass_preexpt_survey %>%
  select(-quadrat.location)%>%
  select(-date)

survey2_eg$Sample_time <- as.character(survey2_eg$Sample_time)
survey2_eg$Sample_time[survey2_eg$Sample_time == "July"] <- "2"
survey2_eg$Sample_time <- as.character(survey2_eg$Sample_time)
survey2_eg$Sample_time[survey2_eg$Sample_time == "June"] <- "1"
survey2_eg$Sample_time <- as.numeric(survey2_eg$Sample_time)

survey2_eg$Sample_mo <- survey2_eg$Sample_time
survey2_eg$Sample_mo[(survey2_eg$Sample_mo)=="1"] <- "June"
survey2_eg$Sample_mo[(survey2_eg$Sample_mo)=="2"] <- "July"

survey2_eg <- survey2_eg %>% 
  mutate(ratio = as.numeric(smithora.dry.weight.grams)/zostra.final.dry.macro.weight.grams)

survey2_eg_July <- survey2_eg %>% 
  mutate(ratio = as.numeric(smithora.dry.weight.grams)/zostra.final.dry.macro.weight.grams) %>%
  filter(Sample_mo == "July")
```

```{r mean mid sd max function}
## function to estimate sds for boxplots
min.mean.sd.max <- function(x) {
  r <- c(min(x), mean(x) - sd(x), mean(x), mean(x) + sd(x), max(x))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}
```

## survey results for Z density

```{r Fig A2C shoots by dry mass regression}
plot(number.shoots.quadrat ~ zostra.final.dry.macro.weight.grams, data = survey2_eg)

shoots.drywt <- ggplot(survey2_eg, aes(x = zostra.final.dry.macro.weight.grams, y = number.shoots.quadrat)) + 
  geom_point(aes(x = zostra.final.dry.macro.weight.grams, y = number.shoots.quadrat), size = 3) +
  scale_y_continuous(name = expression(paste("Zostera Shoots (N/", sample, ")")), limits = c(0, 15)) +
  scale_x_continuous(name = expression("Zostera shoot weight (g/sample)"), limits = c(0, 30)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) + 
  xlab(expression("Zone")) 
  #theme(axis.title.x = element_text(vjust = -1, size = 11)) + 
  #theme(axis.title.y = element_text(vjust = 2, size = 11))

shoots.drywt
ggsave("shoots.drywt.jpg", plot = shoots.drywt, width = 3, height = 3)

mod1 <- lm(number.shoots.quadrat ~ zostra.final.dry.macro.weight.grams, data = survey2_eg)
mod2 <- lm(number.shoots.quadrat ~ 1, data = survey2_eg)
anova(mod1, mod2)
```

A) Shoot density
```{r TABLE 4A survey shoot density models}
hist(survey2_eg$number.shoots.quadrat)
moda <- lm(number.shoots.quadrat ~ 1, data = survey2_eg)
modb <- lm(number.shoots.quadrat ~ 1 + Zone, data = survey2_eg)
modc <- lm(number.shoots.quadrat ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(number.shoots.quadrat ~ 1 + Zone*Sample_time, data = survey2_eg)
model.sel(moda, modb, modc, modd)
mavg <- model.avg(modd, modb, moda)

summary(modd)

Z.june.edge <- coef(mavg)[1]*16
Z.jul.edge <- coef(mavg)[1]*16 + coef(mavg)[3]*16
Z.jul.int <- coef(mavg)[1]*16 + coef(mavg)[4]*16


```

#FIGURE 2: ZOSTERA, SMITHORA and GRAZER ABUNDANCE at transplant sites before experiment
## 2A) Zostera shoot density
```{r Fig 2A shoot density plot}
shoot.density <- ggplot(survey2_eg, aes(x = Zone, y = number.shoots.quadrat*16)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  geom_boxplot(size = 0.75, fill = "transparent") + 
  scale_y_continuous(name = expression(paste("Zostera Shoots (N/", m^2, ")")), limits = c(0, 200)) +
  theme_bw() + 
  theme(panel.grid = element_blank()) + 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  #xlab(expression("Zone")) + 
  #geom_text(label = "A", x = 2.4, y = 15) +
  #theme(axis.title.x = element_text(vjust = -1, size = 10)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 10))

shoot.density

ggsave("shoot.density.jpg", plot = shoot.density, width = 5, height = 2)
```

## 2B) Zostera shoot dry weight
```{r Zostera dry weight figure}
shoot.dwt <- ggplot(survey2_eg, aes(x = Zone, y = zostra.final.dry.macro.weight.grams*16)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent", lwd = 0.75) + 
  scale_y_continuous(name = expression(paste("Zostera shoot weight (g/", m^2, ")")), limits = c(0, 400)) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  theme_bw() + 
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  theme(panel.grid = element_blank()) + 
  #xlab(expression("Zone")) + 
  #geom_text(label = "A", x = 2.4, y = 30) +
  #theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 10))

shoot.dwt
ggsave("shoot.dwt.jpg", plot = shoot.dwt, width = 5, height = 2)
```

## Zostera above ground dry weight
```{r TABLE 4B Zostera dry weight models}
#hist(compare_edge2$total.dry.macro.weight)
hist(survey2_eg$zostra.final.dry.macro.weight.grams)
moda <- lm(zostra.final.dry.macro.weight.grams ~ 1, data = survey2_eg)
modb <- lm(zostra.final.dry.macro.weight.grams ~ 1 + Zone, data = survey2_eg)
modc <- lm(zostra.final.dry.macro.weight.grams ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(zostra.final.dry.macro.weight.grams ~ 1 + Zone*Sample_time, data = survey2_eg)
model.sel(moda, modb, modc, modd)

summary(modc)
Zjune.edge <- (coef(modc)[1] + coef(modc)[3])*16
Zjul.edge <- (coef(modc)[1] + coef(modc)[3]*2)*16
Zjune.int <- (coef(modc)[1] + coef(modc)[3] + coef(modc)[2])*16
Zjul.int <- (coef(modc)[1] + coef(modc)[3]*2 + coef(modc)[2])*16
```

## 2C) Smithora load (dry weight)
```{r TABLE 4C Smithora load models}
#hist(compare_edge2$total.dry.macro.weight)
mod1 <- lm((smithora.dry.weight.grams/zostra.final.dry.macro.weight.grams) ~ site, data = survey2_eg)
anova(mod1)

hist(log(survey2_eg$ratio))

moda <- lm(ratio ~ 1, data = survey2_eg)
modb <- lm(ratio ~ 1 + Zone, data = survey2_eg)
modc <- lm(ratio ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(ratio ~ 1 + Zone*Sample_time, data = survey2_eg)
model.sel(moda, modb, modc, modd)

mavg <- model.avg(modd, modb, moda)

summary(modb)

Z.june.edge <- coef(mavg)[1]*16
Z.jul.edge <- coef(mavg)[1]*16 + coef(mavg)[3]*16
Z.jul.int <- coef(mavg)[1]*16 + coef(mavg)[4]*16
```

```{r Smithora load plot}
smithora <- ggplot(survey2_eg, aes(x = Zone, y = ratio)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent", lwd = 0.75) + 
  scale_y_continuous(name = expression(paste(italic("Smithora"), " (g / g Zostera)")), limits = c(0, 0.5)) +
  theme_bw() + 
   #theme(axis.title.x=element_blank(),
    #    axis.text.x=element_blank(),
     #   axis.ticks.x=element_blank()) +
  facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  theme(panel.grid = element_blank()) + 
  xlab(expression("Zone")) + 
  #geom_text(label = "B", x = 2.4, y = 0.5) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 10))

smithora

ggsave("smithora.jpg", plot = smithora, width = 5, height = 2)
```

### Table 5
```{r TABLE 5 models for smithora load - with zostera density and weight}
moda <- lm(ratio ~ 1, data = survey2_eg)
modb <- lm(ratio ~ 1 + Zone, data = survey2_eg)
modc <- lm(ratio ~ 1 + Zone + Sample_time, data = survey2_eg)
modd <- lm(ratio ~ 1 + Zone*Sample_time, data = survey2_eg)
modf <- lm(ratio ~ 1 + Zone*Sample_time + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = survey2_eg)
modh <- lm(ratio ~ 1 + Zone + Sample_time + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = survey2_eg)
modi <- lm(ratio ~ 1 + Zone + Sample_time + zostra.final.dry.macro.weight.grams, data = survey2_eg)
modj <- lm(ratio ~ 1 + Zone + Sample_time + number.shoots.quadrat, data = survey2_eg)
modn <- lm(ratio ~ 1 + number.shoots.quadrat, data = survey2_eg)
modo <- lm(ratio ~ 1 + zostra.final.dry.macro.weight.grams, data = survey2_eg)
model.sel(moda, modb, modc, modd, modf, modh, modi, modj, modn, modo)
```

```{r TABLE 5 (not published) models for smithora load - with zostera weight}
gpg <- combined$gpgG
moda <- lm(ratio ~ 1, data = combined)
modb <- lm(ratio ~ 1 + Zone.y, data = combined)
modc <- lm(ratio ~ 1 + Zone.y + Sample_time.x, data = combined)
modd <- lm(ratio ~ 1 + Zone.y*Sample_time.x, data = combined)
mode <- lm(ratio ~ 1 + Zone.y*Sample_time.x + gpg, data = combined)
modf <- lm(ratio ~ 1 + Zone.y*Sample_time.x + gpg + zostra.final.dry.macro.weight.grams, data = combined)
modg <- lm(ratio ~ 1 + Zone.y + Sample_time.x + gpg + zostra.final.dry.macro.weight.grams, data = combined)
modh <- lm(ratio ~ 1 + Zone.y + Sample_time.x + zostra.final.dry.macro.weight.grams, data = combined)
modi <- lm(ratio ~ 1 + Zone.y + Sample_time.x + zostra.final.dry.macro.weight.grams, data = combined)
modj <- lm(ratio ~ 1 + Zone.y + Sample_time.x, data = combined)
modk <- lm(ratio ~ 1 + Zone.y + Sample_time.x + gpg, data = combined)
modl <- lm(ratio ~ 1 + Zone.y + gpg, data = combined)
modm <- lm(ratio ~ 1 + gpg, data = combined)
modo <- lm(ratio ~ 1 + zostra.final.dry.macro.weight.grams, data = combined)
modp <- lm(ratio ~ 1 + gpg + zostra.final.dry.macro.weight.grams + number.shoots.quadrat, data = combined)
model.sel(moda, modb, modc, modd, mode, modf, modg, modh, modi, modj, modk, modl, modm, modo, modp)
```



## 2D) GRAZER ABUNDANCE
### Coreen's invert data - organize and combine
```{r }
grazers_coreen1 <- grazers_coreen %>%
  filter(ASU.reference == "eelgrass") %>%
  select(-transect.location)%>%
  select(-days.since.start) %>%
  select(-sieve.size) %>%
  select(-ASU.reference) %>%
  select(-date)

grazers_coreen1 <- grazers_coreen1[,-(45:61)]

gr_coreen2 <- melt(grazers_coreen1, id = c(1,2))
names(gr_coreen2) <- c("Zone","Site", "Species", "Abundance")
gr_coreen3<- ddply(gr_coreen2, .(Zone, Site, Species), summarise, sum(Abundance))
gr_coreen3$N <- gr_coreen3[,4]
inverts <- gr_coreen3

inverts2 <- merge(inverts, grazer_taxa, by.x = "Species", by.y = "taxon.name")
inverts2 <- inverts2[,-4]
inverts_table <- ddply(inverts, .(Site, Zone), summarise, sum(N))
names(inverts_table) <- c("Site", "Zone","inverts_N")

grazers4 <- inverts2 %>%
  filter(grazer == "y")

grazers_table <- ddply(grazers4, .(Site, Zone), summarise, sum(N))
names(grazers_table) <- c( "Site", "Zone","grazers_N")

grazers_gastropod <- grazers4 %>%
  filter(phylum == "mollusca")
gastropod_table <- ddply(grazers_gastropod, .(Site, Zone), summarise, sum(N))
names(gastropod_table) <- c("Site", "Zone","gastro_N")

grazers_crustacean <- grazers4 %>%
  filter(phylum == "arthropoda")
crustacean_table <- ddply(grazers_crustacean, .(Site, Zone), summarise, sum(N))
names(crustacean_table) <- c("Site", "Zone","crust_N")

space_comp <- inverts2 %>%
  filter(Species == "mytilus", phylum == "bryozoa")

inverts_table <- ddply(inverts, .(Site, Zone), summarise, sum(N))
names(inverts_table) <- c("Site", "Zone","inverts_N")
```

### combine invert data with shoot data - Coreen's data
```{r}
combined <- merge(survey2_eg_July, inverts_table, by.x = c("Zone","sample.id"), by.y = c("Zone", "Site"), no.dups = TRUE)

combined <- combined %>% 
  mutate(gpgT = inverts_N/zostra.final.dry.macro.weight.grams)
combined2 <- merge(combined, grazers_table, by.x = c("Zone","sample.id"), by.y = c("Zone", "Site"), no.dups = TRUE)
combined3 <- merge(combined2, gastropod_table, by.x = c("Zone","sample.id"), by.y = c("Zone", "Site"), no.dups = TRUE, suffixes = c(".c", ".g"))
combined4 <- merge(combined3, crustacean_table, by.x = c("Zone","sample.id"), by.y = c("Zone", "Site"), no.dups = TRUE, suffixes = c(".t", ".cr"))

combined <- combined4 %>% 
  mutate(gpgT = inverts_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgG = grazers_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgGa = gastro_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgC = crust_N/zostra.final.dry.macro.weight.grams)
```

```{r total grazers coreen's data - July only}
invertsC <- ggplot(combined, aes(x = Zone, y = gpgT)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Invertebrates (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 10))

invertsC
ggsave("InvertspgC.jpg", plot = invertsC, width = 2.5, height = 2)
```

### invertebrate data processing - Gwen's data, no longer used
```{r} 
#found i think the final grazer file in an email from coreen; using that here and cleaning it.
# I can match the grazer data with the eelgrass data from the same plots!
grazers[is.na(grazers)] <- 0
grazers1 <- grazers %>%
  filter(Seagrass.ASU != "ASU") %>%
  #select(-month_replicate_meadow.position) %>%
  select(-Seagrass.ASU) %>%
  select(-Distance.along.transect..m.)%>%
  select(-identifyer)%>%
  select(-Date.collected)%>%
  select(-size..mm.)
grazers1 <- melt(grazers1, id = c(1,2,3,4))
names(grazers1) <- c("Sample_ID","Sample_time", "Site", "Zone", "Species", "Abundance")
grazers3 <- ddply(grazers1, .(Sample_ID, Site, Zone, Sample_time, Species), summarise, sum(Abundance))
grazers3$N <- grazers3[,6]
inverts <- grazers3
inverts2 <- merge(inverts, grazer_taxa, by.x = "Species", by.y = "taxon.name")
inverts2 <- inverts2[,-6]
inverts_table <- ddply(inverts, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(inverts_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","inverts_N")

grazers4 <- inverts2 %>%
  filter(grazer == "y")

grazers_table <- ddply(grazers4, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(grazers_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","grazers_N")

grazers_gastropod <- grazers4 %>%
  filter(phylum == "mollusca")
gastropod_table <- ddply(grazers_gastropod, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(gastropod_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","gastro_N")

grazers_crustacean <- grazers4 %>%
  filter(phylum == "arthropoda")
crustacean_table <- ddply(grazers_crustacean, .(Sample_ID, Site, Zone, Sample_time), summarise, sum(N))
names(crustacean_table) <- c("Sample_ID", "Site", "Zone", "Sample_time","crust_N")

space_comp <- inverts2 %>%
  filter(Species == "mytilus", phylum == "bryozoa")

#names(grazers4) <- c("Sample_ID", "Site", "Zone", "Sample_time", "Species", "Abundance")

```

```{r combine invert data with shoot data - Gwen's data}
# ok now merge grazer file with the eelgrass file
combined <- merge(survey2_eg, inverts_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", no.dups = TRUE)
combined2 <- merge(combined, grazers_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", no.dups = TRUE)
combined3 <- merge(combined2, gastropod_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", suffixes = c(".c", ".g"))
combined4 <- merge(combined3, crustacean_table, by.x = "month_replicate_meadow.position", by.y = "Sample_ID", suffixes = c(".t", ".cr"))

combined <- combined4 %>% 
  mutate(gpgT = inverts_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgG = grazers_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgGa = gastro_N/zostra.final.dry.macro.weight.grams) %>%
  mutate(gpgC = crust_N/zostra.final.dry.macro.weight.grams)

```

```{r plots for combined factors}
plot(number.shoots.quadrat ~ zostra.final.dry.macro.weight.grams, data = survey2_eg)
mod1 <- lm(number.shoots.quadrat ~ zostra.final.dry.macro.weight.grams, data = survey2_eg)
mod2 <- lm(number.shoots.quadrat ~ 1, data = survey2_eg)
anova(mod1, mod2)

plot(gpgT ~ zostra.final.dry.macro.weight.grams, data = combined)

plot(gpgT ~ number.shoots.quadrat, data = combined)
mod1 <- lm(gpgT ~ number.shoots.quadrat,  data = combined)
mod2 <- lm(gpgT ~ 1,  data = combined)
anova(mod1, mod2)
```


### invert data analysis - figure legend 2, Figure 2A, table 4
```{r}
mod1 <- lm(gpgT ~ zostra.final.dry.macro.weight.grams,  data = combined)
mod2 <- lm(gpgT ~ 1,  data = combined)
anova(mod1, mod2)

mod1a <- lm(gpgT ~ Zone,  data = combined)
mod2a <- lm(gpgT ~ 1,  data = combined)
anova(mod1a, mod2a)
summary(mod2a)
model.sel(mod1a, mod2a)

mod1b <- lm(gpgG ~ Zone,  data = combined)
mod2b <- lm(gpgG ~ 1,  data = combined)
anova(mod1b, mod2b)
summary(mod1b)
model.sel(mod1b, mod2b)

mod1c <- lm(gpgGa ~ Zone,  data = combined)
mod2c <- lm(gpgGa ~ 1,  data = combined)
anova(mod1c, mod2c)
summary(mod1c)

mod1d <- lm(gpgC ~ Zone,  data = combined)
mod2d <- lm(gpgC ~ 1,  data = combined)
anova(mod1d, mod2d)
summary(mod1d)
model.sel(mod1d, mod2d)
```

## Figure A1: additional invert plots and stats
```{r invert plots}
#hist(log(combined$Abundance))
FigA2grazers <- ggplot(combined, aes(x = Zone, y = gpgT)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Invertebrates (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigA
ggsave("FigA2Grazers.jpg", plot = grazerfigA, width = 6, height = 2.5)

grazerfigB <- ggplot(combined, aes(x = Zone, y = gpgGa)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Gastropod Grazers (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigB
ggsave("Gastropods.jpg", plot = grazerfigC, width = 6, height = 2.5)

grazerfigC <- ggplot(combined, aes(x = Zone, y = gpgC)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Crustaceans Grazers (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("Zone")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazerfigC
ggsave("Crustaceans.jpg", plot = grazerfigD, width = 6, height = 2.5)
```

```{r TABLE 4D invert models - Gwen's data}
moda <- lm(gpgT ~ 1, data = combined)
modb <- lm(gpgT ~ 1 + Zone.y, data = combined)
modc <- lm(gpgT ~ 1 + Zone.y + Sample_time.x, data = combined)
modd <- lm(gpgT ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(moda, modb, modc, modd)
mavg <- model.avg(modd, moda)
summary(mavg)
summary(modd)

modGa <- lm(gpgG ~ 1, data = combined)
modGb <- lm(gpgG ~ 1 + Zone.y, data = combined)
modGc <- lm(gpgG ~ 1 + Zone.y + Sample_time.x, data = combined)
modGd <- lm(gpgG ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(modGa, modGb, modGc, modGd)
mavGg <- model.avg(modGd, modGa)
summary(mavGg)
summary(modGd)

modCa <- lm(gpgC ~ 1, data = combined)
modCb <- lm(gpgC ~ 1 + Zone.y, data = combined)
modCc <- lm(gpgC ~ 1 + Zone.y + Sample_time.x, data = combined)
modCd <- lm(gpgC ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(modCa, modCb, modCc, modCd)
mavCg <- model.avg(modCd, modCa)
summary(mavCg)
summary(modCd)

modGaa <- lm(gpgGa ~ 1, data = combined)
modGab <- lm(gpgGa ~ 1 + Zone.y, data = combined)
modGac <- lm(gpgGa ~ 1 + Zone.y + Sample_time.x, data = combined)
modGad <- lm(gpgGa ~ 1 + Zone.y*Sample_time.x, data = combined)
model.sel(modGaa, modGab, modGac, modGad)
mavGag <- model.avg(modGad, modGaa)
summary(mavCg)
summary(modGab)
```



## Figure 2D: Grazer N / Zostera g
```{r}
grazer.zost <- ggplot(combined, aes(x = Zone, y = gpgG)) + 
  geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
  stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
  scale_y_continuous(name = "Grazers (N / g Zostera)") + #limits = c(0, 0.5)
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("Zone")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 14)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 10))

grazer.zost
ggsave("grazer.zost.jpg", plot = grazer.zost, width = 5, height = 2.2)

#analysis

```


## 2E) Grazer diveristy - Coreen's data
```{r}
## create a plot x species matrix
inverts5 <- inverts[,-4]
inverts6 <- inverts5 %>%
  mutate(sample_ID = paste(Zone, Site)) %>%
  select(-Zone) %>%
  select(-Site)

inverts_7 <- as.data.frame(inverts6, row.names(inverts6$sample_ID))
#inverts_com <- inverts_7[,-3]

inverts_Jcom <- dcast(inverts_7, sample_ID ~ Species, value.var = "N")

#estimate relative abundance:
Jcom.rel <-         
  decostand(inverts_Jcom[,-(1)], method = "total")

#calculate distance matrix
Jcom_distmat <- 
  vegdist(Jcom.rel, method = "bray")

# Creating easy to view matrix and writing .csv
Jcom_distmat <- 
  as.matrix(Jcom_distmat, labels = T)
write.csv(Jcom_distmat, "July_communities_distmat.csv")

# create grouping data
sites <- c("edge a", "edge b", "edge c", "edge d", "edge e", "edge f", "inner a", "inner b", "inner c", "inner d", "inner e", "inner f")
zones <- c("Edge", "Edge", "Edge", "Edge", "Edge", "Edge", "Inner", "Inner","Inner","Inner",  "Inner", "Inner")
sitezones <- as.data.frame(cbind(sites, zones))

# run ndms
Jcom_NMS <-
  metaMDS(Jcom_distmat,
          distance = "bray",
          k = 2,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE, 
          points = sites)
```

###grazer diversity ggplot
```{r}
# plot it on ggplot
data.scores <- as.data.frame(scores(Jcom_NMS))
data.scores$site <- rownames(data.scores)
data.scores$grp <- zones

div.plot <- ggplot(data = data.scores) +
  stat_ellipse(aes(x=NMDS1, y = NMDS2, group = zones), level = 0.50) +
  geom_point(aes(x=NMDS1, y=NMDS2, shape = zones, colour = zones), size = 2) +
  scale_colour_manual(values=c("black", "gray50"),
                      name="Zone:",
                    breaks=c("Edge", "Inner"),
                    labels=c("edge", "interior")) +
  scale_shape_manual(values=c(16, 17),
                     name="Zone:",
                    breaks=c("Edge", "Inner"),
                    labels=c("edge", "interior")) +
  theme_bw() + 
  theme(panel.grid = element_blank(),
    legend.title = element_text(size=10), 
    legend.text = element_text(size=9),
    legend.position="bottom") +
  theme(axis.title.x = element_text(vjust = -1, size = 10)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 10))

div.plot
ggsave("div.plot.jpg", plot = div.plot, width = 2.5, height = 3)
```
## adonis
```{r}
adon.results <- adonis(Jcom_distmat ~ sitezones$zones, permutations = 999, method = "bray")
print(adon.results)
```

### nmds base plot - not using anymore
```{r}
stressplot(Jcom_NMS)

plot(Jcom_NMS, display = ("sites"), type = "n") 
orditorp(Jcom_NMS, "sites") 

pchvec <- c(17, 16)

jpeg('JulyNMDS.jpg')
plot(Jcom_NMS, display = ("sites"), type = "n")
with(sitezones, 
     points(Jcom_NMS,
            display = "sites", 
            col = "black",
            pch = pchvec[zones]))

ordihull(
  Jcom_NMS,
  sitezones$zones,
  display = "sites",
  draw = c("polygon"),
  col = NULL,
  border = c("gray0", "gray48"),
  lty = c(1, 2),
  lwd = 1
  )

scrs <-
  scores(Jcom_NMS, display = "sites")
cent <-
  aggregate(scrs ~ zones, data = sitezones, FUN = "mean")
names(cent) [-1] <- colnames(scrs)
points(cent [,-1],
       pch = c( 8 , 8),
       col = c("gray0", "gray48"),
       bg = c("black"),
       lwd = 2.0,
       cex = 1.0 # Plots centroids as points on ordination
       )

dev.off()

spp_scrs <- sppscores(Jcom_NMS) <- Jcom.rel
plot(Jcom_NMS, "sites")
plot(Jcom_NMS, "species") 
orditorp(Jcom_NMS, "species")
```

### Old plots and analyses with Gwen's data

## Figure: Smithora load / Grazer load - not currently using 
```{r grazers and smithora plot}
grazersmith <- ggplot(combined, aes(x = gpgG, y = ratio)) + #color = Sample_mo
  geom_point(size=3) +
  theme_bw() + 
  theme(panel.grid = element_blank()) +
  #facet_grid( ~ fct_rev(Sample_mo), scale = "free") +
  xlab(expression("grazers / g Zostera")) + 
  ylab(expression("Smithora g / g Zostera")) + 
  #geom_text(label = "C", x = 2.4, y = 650) +
  theme(axis.title.x = element_text(vjust = -1, size = 12)) + 
  theme(axis.title.y = element_text(vjust = 2, size = 12))

grazersmith
ggsave("Grazers_smith.jpg", plot = grazersmith, width = 3, height = 3)

mod1 <- lm(combined$ratio ~ combined$gpgG)
mod2 <- lm(combined$ratio ~ 1)
model.sel(mod1, mod2)
anova(mod1)
summary(mod1)
```



## Grazer diversity - July only
```{r}
## create a plot x species matrix
inverts5 <- inverts[,-6]
inverts6 <- inverts5[(inverts5$Sample_time == "July"),]
inverts_July <- inverts6[,-(3:4)]
inverts_July <- inverts_July[,-(1)]
inverts_July <- as.data.frame(inverts_July, row.names(inverts_July$Sample_ID))
inverts_Jcom <- dcast(inverts_July, Site ~ Species)

#estimate relative abundance:
Jcom.rel <-         
  decostand(inverts_Jcom[,-(1)], method = "total")

#calculate distance matrix
Jcom_distmat <- 
  vegdist(Jcom.rel, method = "bray")

# Creating easy to view matrix and writing .csv
Jcom_distmat <- 
  as.matrix(Jcom_distmat, labels = T)
write.csv(Jcom_distmat, "July_communities_distmat.csv")

# create grouping data
sites <- c("Wolf edge A", "wolf edge D", "wolf edge F", "Wolf inner A", "Wolf Inner C", "Wolf Inner D", "Wolf inner F")
zones <- c("Edge", "Edge", "Edge", "Inner", "Inner","Inner","Inner")
sitezones <- as.data.frame(cbind(sites, zones))

# run ndms
Jcom_NMS <-
  metaMDS(Jcom_distmat,
          distance = "bray",
          k = 2,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE, 
          points = sites)

stressplot(Jcom_NMS)

plot(Jcom_NMS, display = ("sites"), type = "n") 
orditorp(Jcom_NMS, "sites") 

pchvec <- c(17, 16)

jpeg('JulyNMDS.jpg')

plot(Jcom_NMS, type = "n")
with(sitezones, 
     points(Jcom_NMS,
            display = "sites", 
            col = "black",
            pch = pchvec[zones]))
dev.off()

```

## Grazer diversity - June only
```{r}
## create a plot x species matrix; this still has ASUs and Controls, i don't know what controls mean in this context so we should not use June data i guess. 
inverts6 <- inverts5[(inverts5$Sample_time == "June"),]
inverts_June <- inverts6[,-(3:4)]
inverts_June <- inverts_June[,-(1)]
inverts_June <- as.data.frame(inverts_June, row.names(inverts_June$Sample_ID))
inverts_Jncom <- dcast(inverts_June, Site ~ Species)


#https://rpubs.com/CPEL/NMDS
#estimate relative abundance:
Jncom.rel <-         
  decostand(inverts_Jncom[,-(1)], method = "total")

#calculate distance matrix
Jncom_distmat <- 
  vegdist(Jncom.rel, method = "bray")

# Creating easy to view matrix and writing .csv
Jncom_distmat <- 
  as.matrix(Jncom_distmat, labels = T)
write.csv(Jncom_distmat, "July_communities_distmat.csv")

# create grouping data
sites <- c(levels(inverts_June$Site))  
zones <- c("Edge", "Edge", "Edge", "Inner", "Inner","Inner","Inner")
sitezones <- as.data.frame(cbind(sites, zones))

# run ndms
Jcom_NMS <-
  metaMDS(Jcom_distmat,
          distance = "bray",
          k = 2,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE, 
          points = sites)

stressplot(Jcom_NMS)

plot(Jcom_NMS, display = ("sites"), type = "n") 
orditorp(Jcom_NMS, "sites") 

pchvec <- c(17, 16)

jpeg('JulyNMDS.jpg')

plot(Jcom_NMS, type = "n")
with(sitezones, 
     points(Jcom_NMS,
            display = "sites", 
            col = "black",
            pch = pchvec[zones]))
dev.off()

```

## Grazer diversity - all
```{r}
inverts_all <- inverts5[,-(3:4)]
#inverts_all <- inverts_all[,-(1)]
inverts_all <- as.data.frame(inverts_all, row.names(inverts_all$Sample_ID))
inverts_Tcom <- dcast(inverts_all, Site ~ Species)


Tcom.rel <-         
  decostand(inverts_Tcom[,-(1)], method = "total")

#calculate distance matrix
Tcom_distmat <- 
  vegdist(Tcom.rel, method = "bray")

# Creating easy to view matrix and writing .csv
Tcom_distmat <- 
  as.matrix(Tcom_distmat, labels = T)
write.csv(Tcom_distmat, "communities_distmat.csv")

# create grouping data
sites_oldnames <- c("july_-120_edge", "july_-120_inner", "july_-160_edge", "july_-40_inner", "july_-80_inner", "july_0_inner", "july_40_edge", "june_-120_edge", "june_-120_inner", "june_-40_edge", "june_-40_inner", "june_-80_edge", "june_-80_inner", "june_0_edge", "june_0_inner", "june_40_edge", "june_40_inner")
sites_standardnames <- c("Edge D", "Inner E", "Edge A","Inner D",  "Edge C", "Inner A", "Edge F", "Edge D","Inner F", "Edge B",  "Inner B", "Edge C", "Inner C", "Edge E", "Inner A", "Edge B",  "Inner B") #i assumed here that the -80 inner, etc, referred to the same sites in June and July. I suspect this is incorrect... so maybe i won't proceed with this. 
zones <- c("Edge", "Inner", "Edge","Inner","Inner","Inner", "Edge","Edge", "Inner", "Edge","Inner","Edge","Inner","Edge","Inner","Edge","Inner")
month <- c("July", "July", "July","July", "July", "July","July", "June","June","June","June","June","June","June","June","June","June")
sitezonesA <- as.data.frame(cbind(sites_oldnames, sites_standardnames, zones, month))

# run ndms
Tcom_NMS <-
  metaMDS(Tcom_distmat,
          distance = "bray",
          k = 2,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE, 
          points = sites_standardnames)

stressplot(Tcom_NMS)

plot(Tcom_NMS) 
orditorp(Tcom_NMS, "sites") 

pchvec <- c(17, 16)
colvec <- c("gray49", "black")

jpeg('allNMDS.jpg')

plot(Tcom_NMS, type = "n")
with(sitezonesA, 
     points(Tcom_NMS,
            display = "sites", 
            col = colvec[month],
            pch = pchvec[zones]))

dev.off()

#Create convex hulls that highlight point clusters based on grouping dataframe
ordihull(
  Tcom_NMS,
  sitezonesA$zones,
  display = "sites",
  draw = c("polygon"),
  col = NULL,
  border = c("gray0", "gray0", "gray48", "gray48"),
  lty = c(1, 2, 1, 2),
  lwd = 1
  )

ordihull(
  Tcom_NMS,
  sitezonesA$month,
  display = "sites",
  draw = c("polygon"),
  col = NULL,
  border = c("gray0", "gray0", "gray48", "gray48"),
  lty = c(1, 2, 1, 2),
  lwd = 1
  )
```


## FIGURE 3: Smithora results post experiment - remake this figure. april 5th: i'm not sure if it still needs to be remade - i have to check this.
```{r experiment results}
smith.expt$Source <- revalue(smith.expt$Source, c("Edge"="Edge (high Smithora)",  "Interior"="Interior (low Smithora)"))
smith.expt$Source <- as.factor(smith.expt$Source)
smith.expt$Type <- revalue(smith.expt$Category.in.transplant, c("Ambient"="Unmanip.", "Experiment"="Transplanted", "Control"="Control"))
smith.expt$Type <- as.factor(smith.expt$Type)
smith.expt$ratio <- smith.expt$Ratio.smithora.leaves
smith.expt$Final.Zone <- smith.expt$Final.Location

experiment <- ggplot(smith.expt[(smith.expt$Type != "Unmanip."),], aes(x = Type, y = ratio)) + 
geom_jitter(position = position_jitter(width=.2), size=3, colour = "gray60") +
stat_summary(fun.data = min.mean.sd.max, geom = "boxplot", fill = "transparent") + 
facet_wrap(~Source) + 
theme_bw() + 
theme(panel.grid = element_blank()) + 
theme(strip.background = element_rect(fill="white")) + 
scale_y_continuous(name = expression(paste(italic("Smithora"), " (g dry wt / g Zostera dry wt)")), limits = c(-0.1, 1), breaks = c(0, 0.5, 1), labels = c(0, 0.5, 1)) +
xlab("") +
labs(title = "Site of Experimental Planting") 

experiment
ggsave("experiment.jpg", plot = experiment, width = 6, height = 3)
```

##Experimental analysis: 

#first analyze control vs unmanipulated
```{r}
hist((smith.expt[(smith.expt$Type != "Transplanted"),]$ratio))
mod1 <- lm((smith.expt[(smith.expt$Type != "Transplanted"),]$ratio) ~ smith.expt[(smith.expt$Type != "Transplanted"),]$Type + smith.expt[(smith.expt$Type != "Transplanted"),]$Source)
anova(mod1)
```

```{r two way anova}
mod1 <- lm()
```

# then analyze control v transplanted
```{r}
hist(log(smith.expt[(smith.expt$Type != "Unmanip."),]$ratio + 1))
mod2 <- lm(log(ratio + 1) ~ Type*Source, data = smith.expt[(smith.expt$Type != "Unmanip."),])
summary(mod2)
```
